---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# hubDevs

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/hubDevs)](https://CRAN.R-project.org/package=hubDevs)
[![R-CMD-check](https://github.com/Infectious-Disease-Modeling-Hubs/hubDevs/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Infectious-Disease-Modeling-Hubs/hubDevs/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of hubDevs is to ...

## Installation

You can install the development version of hubDevs from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Infectious-Disease-Modeling-Hubs/hubDevs")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hubDevs)
## basic example code
```

## Code of Conduct

Please note that the hubDevs package is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.


## Contributing

Interested in contributing back to the open-source Hubverse project?
Learn more about how to [get involved in the Hubverse Community](https://hubdocs.readthedocs.io/en/latest/overview/contribute.html) or [how to contribute to the hubDevs package](.github/CONTRIBUTING.md).
